---
title: "Supply-side Concerns - Purchase Limits"
author: "Lieve Heyrman"
date: "2024-07-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r set up file}

rm(list=ls())

library(here)

# set project_path
project_path <- here::here()

# set path to data files (depending on operating computer)
location <- "local"
if (location == "server") {
  if (Sys.info()["nodename"] == "GHUM-L-E939DCHK"){
    data_path <- "X:/Retailing_Group_RawData/Hoarding data"
  }else if (Sys.info()["nodename"] == "GHUM-L-E0376K0Q") {
    data_path <- "X:/Retailing_Group_RawData/Hoarding data" }
} else if (location == "local") { 
  if (Sys.info()["nodename"] == "GHUM-L-E939DCHK"){
    data_path <- ""
  }else if (Sys.info()["nodename"] == "GHUM-L-E0376K0Q") {
    data_path <- "C:/PhD KU Leuven/AiMark" } 
}

# load libraries
list.of.packages <- c("plyr","tidyr","ggplot2", "tidyverse", "zoo", "readxl", "car", "sampleSelection", "stargazer", "haven","expss", "plm", "sandwich", "lmtest")
# Install package if they are not installed yet
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
# Load packages
lapply(list.of.packages, require, character.only = TRUE)

# Suppress summarise info
options(dplyr.summarise.inform = FALSE)

options(scipen = 999)

# create country list
country_list <- c("NL","BE","GE","FR","UK")
# set country
country <- country_list[country_list=="NL"]

```


# JUMBO AND ALBERT HEIJN PURCHASE LIMITS

Our media search revealed that Jumbo and Albert Heijn put a formal limit on the number of toilet paper rolls a household could buy per shopping trip.
To ensure our results are not driven by these limits, we employ a set of robustness checks.
Specifically, we employ 2 robustness checks:   (i) we exclude all households who shopped at Jumbo or Albert Heijn Online after 1 March 2020 (in any category)



### EXCLUDING HOUSEHOLDS WHO SHOPPED AT JUMBO OR ALBERT HEIJN AFTER 1 MARCH 2020 (CURRENTLY NOT IN MANUSCRIPT)


```{r identify all Jumbo and Albert Heijn Online shoppers after 1 March 2020}

# get a list of the households we investigate
load(paste(project_path,"/INC-QUANT model/toilet paper/prepared_purchasedata_NL_final",sep=""))
all.households <- unique(TP_purch$Panelist)
rm(TP_purch)

# load 2020 purchase data
all.purch.2020 <- read.csv(paste(data_path, "/",country, "/purchase_promo_2020.csv", sep = ""))
# only keep purchases of relevant households
all.purch.2020 <- all.purch.2020[all.purch.2020$Panelist %in% all.households,]
# transform Date of Purchase variable
all.purch.2020$Date_of_purchase <- as.Date(all.purch.2020$Date_of_purchase)
# only keep purchases between 1 March 2020 and 30 April 2020
all.purch.2020 <- all.purch.2020[all.purch.2020$Date_of_purchase > as.Date("2020-02-28") & all.purch.2020$Date_of_purchase < as.Date("2020-05-01"),]
# get chains and RestRetailers right
AlbertHeijn_formats <- c("Albert Heijn", "AH XL", "AH to Go", "Albert.nl")
Jumbo_formats <- c("Jumbo", "Jumbo City", "Jumbo Foodmarkt")
all.purch.2020$Banner_name[all.purch.2020$Banner_name %in% AlbertHeijn_formats] <- AlbertHeijn_formats[1]
all.purch.2020$Banner_name[all.purch.2020$Banner_name %in% Jumbo_formats] <- Jumbo_formats[1]
all.purch.2020$Banner_name[!(all.purch.2020$Banner_name %in% AlbertHeijn_formats) & !(all.purch.2020$Banner_name %in% Jumbo_formats)] <- "RestRetailer"

# get all households that buy anything (any category) at Jumbo
HH_Jumbo <- unique(all.purch.2020$Panelist[all.purch.2020$Banner_name == "Jumbo"])
# get all households that buy anything (any category) at Albert Heijn
HH_AH <- unique(all.purch.2020$Panelist[all.purch.2020$Banner_name == "Albert Heijn"])
online <- c("online-bezorgen", "online-ophalen") 
# get all households that buy anything (any category) at Albert Heijn in the online channel
HH_AH_online <- unique(all.purch.2020$Panelist[all.purch.2020$Banner_name == "Albert Heijn" & all.purch.2020$Purchase_method %in% online])

rm(all.purch.2020)


```

``` {r exclude Jumbo or Albert Heijn Online shoppers}

# load prepared dataset
load(paste(project_path,"/INC-QUANT model/toilet paper/FullData_with_moderators_and_labels.RData",sep=""))
# filter dataset
FullData <- FullData[!(FullData$Household %in% HH_Jumbo) & !(FullData$Household %in% HH_AH_online),]

### TOBIT 2 - HECKMAN SELECTION MODEL ###
# main model
library(modelsummary)
# main effects only, including consumer characteristics as controls (not interacted)
heckman_main <- selection(selection = !is.na(Total_volume_sales) ~  PromoIndex + PanicIndex 
                                      + HouseholdInventory + PriceIndex
                                      + Average_IPT + PromoSensitivity + PLShare + BrandLoyalty
                                      + Age + HouseholdSize + Income + Day_of_week + Week + Year,
                          outcome =          Total_volume_sales  ~  PromoIndex + PanicIndex 
                                      + HouseholdInventory + PriceIndex
                                      + Average_Q + PromoSensitivity + PLShare + BrandLoyalty
                                      + Age + HouseholdSize + Income + Day_of_week + Week + Year,
                          data = FullData, method ="2step")
modelsummary(heckman_main, shape = term + statistic ~ component, stars = T,
             coef_map = c("(Intercept)" = "Intercept", "PanicIndex" = "Panic Index", "PromoIndex" = "Promo Index", "PriceIndex" = "Price Index", "HouseholdInventory" = "Household Inventory", "Average_IPT" = "Average IPT", "Average_Q" = "Average Q", "PromoSensitivity" = "Promo Sensitivity", "PLShare" = "PL Share", "BrandLoyalty" = "Brand Loyalty", "Age" = "Age", "HouseholdSize" = "Household Size", "Income" = "Income"))

rm(heckman_main)
rm(FullData)

```



### EXCLUDING ALBERT HEIJN AND JUMBO SINGLE STORE SHOPPERS

```{r identifying Albert Heijn and Jumbo single store shoppers}

# load all 2018 purchase data
all.purch.2018 <- read.csv(paste(data_path, "/",country, "/purchase_promo_2018.csv", sep = ""))
# only keep relevant households
all.purch.2018 <- all.purch.2018[all.purch.2018$Panelist %in% all.households,]
# get chains and RestRetailers right
AlbertHeijn_formats <- c("Albert Heijn", "AH XL", "AH to Go", "Albert.nl")
Jumbo_formats <- c("Jumbo", "Jumbo City", "Jumbo Foodmarkt")
all.purch.2018$Banner_name[all.purch.2018$Banner_name %in% AlbertHeijn_formats] <- AlbertHeijn_formats[1]
all.purch.2018$Banner_name[all.purch.2018$Banner_name %in% Jumbo_formats] <- Jumbo_formats[1]
chains_keep <- c("Albert Heijn", "Jumbo", "Plus", "Lidl", "Aldi", "DIRK")
all.purch.2018$Banner_name[!all.purch.2018$Banner_name %in% chains_keep] <- "RestRetailer"
# group purchases of same day at same retailer as one trip
all.purch.2018 <- all.purch.2018 %>% group_by(Panelist, Banner_name, Date_of_purchase) %>% summarize(value = sum(Total_value_sales))
# count number of trips per household per chain
all.purch.2018 <- all.purch.2018 %>% group_by(Panelist, Banner_name) %>% summarize(ChainTrips = n())
# get total number of trips per household
all.purch.2018 <- all.purch.2018 %>% group_by(Panelist) %>% mutate(TotalTrips = sum(ChainTrips))
# get share of trips to each chain
all.purch.2018$MS_chain <- all.purch.2018$ChainTrips / all.purch.2018$TotalTrips

# single-store shoppers = more than 80% of trips to that chain
HH_Jumbo_singlestore <- unique(all.purch.2018$Panelist[all.purch.2018$Banner_name == "Jumbo" & all.purch.2018$MS_chain > 0.8])
HH_AH_singlestore <- unique(all.purch.2018$Panelist[all.purch.2018$Banner_name == "Albert Heijn" & all.purch.2018$MS_chain > 0.8])

rm(all.purch.2018)
```

``` {r exclude Jumbo or Albert Heijn single store shoppers}

# load prepared dataset
load(paste(project_path,"/INC-QUANT model/toilet paper/FullData_with_moderators_and_labels.RData",sep=""))
# filter dataset
FullData <- FullData[!(FullData$Household %in% HH_Jumbo_singlestore) & !(FullData$Household %in% HH_AH_singlestore),]

### TOBIT 2 - HECKMAN SELECTION MODEL ###
# main model
library(modelsummary)
# main effects only, including consumer characteristics as controls (not interacted)
heckman_main <- selection(selection = !is.na(Total_volume_sales) ~  PromoIndex + PanicIndex 
                                      + HouseholdInventory + PriceIndex
                                      + Average_IPT + PromoSensitivity + PLShare + BrandLoyalty
                                      + Age + HouseholdSize + Income + Day_of_week + Week + Year,
                          outcome =          Total_volume_sales  ~  PromoIndex + PanicIndex 
                                      + HouseholdInventory + PriceIndex
                                      + Average_Q + PromoSensitivity + PLShare + BrandLoyalty
                                      + Age + HouseholdSize + Income + Day_of_week + Week + Year,
                          data = FullData, method ="2step")
modelsummary(heckman_main, shape = term + statistic ~ component, stars = T,
             #coef_map = c("(Intercept)" = "Intercept", "PanicIndex" = "Panic Index", "PromoIndex" = "Promo Index", "PriceIndex" = "Price Index", "HouseholdInventory" = "Household Inventory", "Average_IPT" = "Average IPT", "Average_Q" = "Average Q", "PromoSensitivity" = "Promo Sensitivity", "PLShare" = "PL Share", "BrandLoyalty" = "Brand Loyalty", "Age" = "Age", "HouseholdSize" = "Household Size", "Income" = "Income"),
             statistic = c("std.error", "p.value"))

rm(heckman_main)
rm(FullData)


```






